The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2019-01-05 pkg/partykit/inst/guideliketest/draft/draft.Rnw
now results are recalculated if not already stored
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2402 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 164d038dfb371f0c5a9c548590ebfde74be694b7

<<preliminaries, echo=FALSE, results=hide>>=
# setwd("~/svn/partykit/pkg/partykit/inst/guideliketest/draft/")
options(prompt = "R> ", continue = "+  ", useFancyQuotes = FALSE, width = 70)
library("partykit")
library("Formula")
library("parallel")
library("lattice")
library("scales")
# setwd("~/svn/partykit/pkg/partykit/inst/guideliketest/draft/")
source("../guidelike.R")
source("../tests_guideprune.R")
#load("../sim/simres20180422_1step.rda")
load("../sim/simres20181223_stump.rda")
sim_stump <- simres$res
#load("../sim/simres20180422_2step.rda")
#sim2step <- simres
rm(simres)
load("../sim/simres20181223_tree.rda")
sim_tree <- simres$res
rm(simres)

@@

<<pruning_data, echo=FALSE, results=hide>>=
load("../sim/simres20181227_pruning.rda")
pr <- simres$res
## extract data for xyplot comparing ARI and ARI_p
pr <- pr[,c(1,2,7,8,9,12,15)]
## extended data set with post-pruning results being represented as separated tests
prex <- pr[,c(1,2,3,4,6)]
prex <- rbind(prex,prex)

>>>>

<<preliminaries, echo=FALSE, results=hide>>=
# setwd("~/svn/partykit/pkg/partykit/inst/guideliketest/draft/")
options(prompt = "R> ", continue = "+  ", useFancyQuotes = FALSE, width = 70)
library("partykit")
library("Formula")
library("parallel")
library("lattice")
library("scales")
# setwd("~/svn/partykit/pkg/partykit/inst/guideliketest/draft/")
source("../guidelike.R")
source("../tests_guideprune.R")

if(file.exists("stump.rda")){
  load("stump.rda")
} else {
  simres <- simwrapper_p(nobs = 250, nrep = 100, seed = 7,
                         nrsplitvar = 1, nrsteps = 1, nrlevels = 2,
                         delta = seq(from = 0, to = 1, by = 0.1),
                         xi = c(0, 0.2, 0.5, 0.8), vary_beta = c("all", "beta0", "beta1"),
                         binary_regressor = FALSE, binary_beta = TRUE, only_intercept = FALSE,
                         test = c("ctree", "mfluc", "ctree_max",
                                  "ctree_cat", "mfluc_cat", "ctree_max_cat",
                                  "ctree_bin", "mfluc_bin", "ctree_max_bin",
                                  "ctree_cat_bin", "mfluc_cat_bin", "ctree_max_cat_bin",
                                  "guide_sum_12", "guide_coin_12", "guide_sum_1_cor"),
                         beta0 = 0, beta1 = 1,
                         stump = TRUE, z1dist = "unif", sigma = 1, alpha = 0.05)

  save(simres, file = "stump.rda")
}
sim_stump <- simres$res
rm(simres)

if(file.exists("tree.rda")){
  load("tree.rda")
} else {
  simres <- simwrapper_p(nobs = 250, nrep = 100, seed = 7,
                       nrsplitvar = 2, nrsteps = 1, nrlevels = 2,
                       delta = seq(from = 0, to = 1, by = 0.1),
                       xi = c(0, 0.2, 0.5, 0.8), vary_beta = "all",
                       binary_regressor = FALSE, binary_beta = TRUE,
                       only_intercept = FALSE,
                       test = c("ctree", "mfluc", "ctree_max",
                                "ctree_cat", "mfluc_cat", "ctree_max_cat",
                                "ctree_bin", "mfluc_bin", "ctree_max_bin",
                                "ctree_cat_bin", "mfluc_cat_bin", "ctree_max_cat_bin",
                                "guide_sum_12", "guide_coin_12", "guide_sum_1_cor"),
                       beta0 = NULL, beta1 = NULL,
                       stump = FALSE, z1dist = "unif", sigma = 1, alpha = 0.05)

  save(simres, file = "tree.rda")
}
sim_tree <- simres$res
rm(simres)

@@

<<pruning_data, echo=FALSE, results=hide>>=
if(file.exists("pruning.rda")){
  load("pruning.rda")
} else {
  simres <- simwrapper_p(nobs = 250, nrep = 100, seed = 7, 
                         nrsteps = 1, nrlevels = 2,
                         delta = seq(from = 0, to = 1, by = 0.1),
                         xi = c(0, 0.2, 0.5, 0.8), 
                         vary_beta = "all", binary_regressor = FALSE,
                         binary_beta = TRUE, only_intercept = FALSE,
                         compare_pruning = TRUE,
                         test = c("ctree", "mfluc",
                                  "guide_sum_12", 
                                  "guide_sum_1_cor"),
                         beta0 = NULL, beta1 = NULL,
                         stump = FALSE, z1dist = "unif", sigma = 1, alpha = 0.05,
                         nrsplitvar = 2)

  save(simres, file = "pruning.rda")  
}

pr <- simres$res
## extract data for xyplot comparing ARI and ARI_p
pr <- pr[,c(1,2,7,8,9,12,15)]
## extended data set with post-pruning results being represented as separated tests
prex <- pr[,c(1,2,3,4,6)]
prex <- rbind(prex,prex)
